Capstone Movielens Report

### 2025-06-01 reports/capstone-movielens.site/04.appendix.Rmd
UMGYDE Model Tuning by `degree` & `span` parameters of the stats::loess function (completed).

The soure code of the [data.plot]() function is shown below:
```{r eval=FALSE}
data.plot <- function(data, 
                      title, 
                      xname, 
                      yname, 
                      xlabel = NULL, 
                      ylabel = NULL,
                      line_col = "blue",
                      normalize = FALSE) {
  y <- data[, yname]

@@

>>>>

The soure code of the [data.plot]((https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) function is shown below:
```{r eval=FALSE}
data.plot <- function(data, 
                      title, 
                      xname, 
                      yname, 
                      xlabel = NULL, 
                      ylabel = NULL,
                      line_col = "blue",
                      normalize = FALSE) {
  y <- data[, yname]

@@

### [data.plot.left.n](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L493) Function {#func.data.plot.left.n}
\

Plots a graph based on the dataset passed in the [data](#func.data.plot.left.n.params.data) parameter, using both points and a line.

::: { #func.data.plot.left.n.Usage .sidebar }
#### Usage
\

```{r eval=FALSE}
data.plot.left.n <- function(data, 
                             left.n = 0,
                             title, 
                             xname, 
                             yname, 
                             xlabel, 
                             ylabel,
                             line_col = "red",
                             normalize = FALSE)
```
:::

::: { #func.data.plot.left.n.params .sidebar }
#### Parameters
\

::: { #func.data.plot.left.n.params.data .sidebar }
  - **data:** Dataset to use for the plot;

:::
::: { #func.data.plot.left.n.params.title .sidebar }
  - **title:** Title of the plot;

:::
::: { #func.data.plot.left.n.params.xname .sidebar }
  - **xname:** The name of the dataset column used as the source of the $x$ variable for the plot;

:::
::: { #func.data.plot.left.n.params.yname .sidebar }
  - **yname:** The name of the dataset column used as the source of the $y$ variable for the plot;

:::
::: { #func.data.plot.left.n.params.xlabel .sidebar }
  - *xlabel = NULL*:** The $x$ axis label. If `NULL`, the value of the `xname` parameter is used for the label;

:::
::: { #func.data.plot.left.n.params.ylabel .sidebar }
  - **ylabel = NULL:** The $y$ axis label. If `NULL`, the value of the `yname` parameter is used for the label.;

:::
::: { #func.data.plot.left.n.params.line_col .sidebar }
  - **line_col = blue:** The line color;

:::
::: { #func.data.plot.left.n.params.normalize .sidebar }
  - **normalize = FALSE:** If `TRUE`, the deviation of $y$ from its mean is used to plot, rather than $y$ values. Otherwise, the value of $y$ is used.

::: { #func.data.plot.left.n.details .sidebar }
#### Details
\

The function is a wrapper for the [data.plot](#func.data.plot) function described above and is a simple and convenient tool for more detailed visualizing the left part of the graph.

::: { #func.data.plot.left.n.code .sidebar }
#### Source Code
\

The soure code of the [data.plot.left.n](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L493) function is shown below:
```{r eval=FALSE}
data.plot.left.n <- function(data, 
                             left.n = 0,
                             title, 
                             xname, 
                             yname, 
                             xlabel, 
                             ylabel,
                             line_col = "red",
                             normalize = FALSE) {
  x_col <- data[, xname] 
  y_col <- data[, yname]

  data.left <- data

  if (left.n > 0) {
    data.left <- data |> 
      head(left.n)
  }

  data.left |>
    data.plot(title = title,
              xname = xname,
              yname = yname,
              xlabel = xlabel,
              ylabel = ylabel,
              line_col = line_col,
              normalize = normalize)
}
```

::: {.noteblock data-latex=""}
The source code of the [data.plot.left.n](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L493) is also available in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L493) script.
:::
:::

### [data.plot.left_detailed](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L448) Function {#func.data.plot.left_detailed}
\

Plots a graph based on the dataset passed in the [data](#func.data.plot.left_detailed.params.data) parameter, using both points and a line.

::: { #func.data.plot.left_detailed.Usage .sidebar }
#### Usage
\

```{r eval=FALSE}
data.plot.left_detailed <- function(data, 
                                    left.n = 0,
                                    title = NULL,
                                    title.left = NULL,
                                    xname, 
                                    yname, 
                                    xlabel1 = NULL, 
                                    xlabel2 = NULL, 
                                    ylabel1 = NULL,
                                    ylabel2 = NULL,
                                    line_col1 = "blue",
                                    line_col2 = "red",
                                    normalize = FALSE)
```
:::

::: { #func.data.plot.left_detailed.params .sidebar }
#### Parameters
\

::: { #func.data.plot.left_detailed.params.data .sidebar }
  - **data:** Dataset to use for the plot;

:::
::: { #func.data.plot.left_detailed.params.title .sidebar }
  - **title:** Title of the plot;

:::
::: { #func.data.plot.left_detailed.params.xname .sidebar }
  - **xname:** The name of the dataset column used as the source of the $x$ variable for the plot;

:::
::: { #func.data.plot.left_detailed.params.yname .sidebar }
  - **yname:** The name of the dataset column used as the source of the $y$ variable for the plot;

:::
::: { #func.data.plot.left_detailed.params.xlabel .sidebar }
  - *xlabel = NULL*:** The $x$ axis label. If `NULL`, the value of the `xname` parameter is used for the label;

:::
::: { #func.data.plot.left_detailed.params.ylabel .sidebar }
  - **ylabel = NULL:** The $y$ axis label. If `NULL`, the value of the `yname` parameter is used for the label.;

:::
::: { #func.data.plot.left_detailed.params.line_col .sidebar }
  - **line_col = blue:** The line color;

:::
::: { #func.data.plot.left_detailed.params.normalize .sidebar }
  - **normalize = FALSE:** If `TRUE`, the deviation of $y$ from its mean is used to plot, rather than $y$ values. Otherwise, the value of $y$ is used.

::: { #func.data.plot.left_detailed.details .sidebar }
#### Details
\

The function is a wrapper for the [data.plot.left.n](#func.data.plot.left.n) function described above and is a simple and convenient tool for more detailed visualizing the left part of the graph.

::: { #func.data.plot.left_detailed.code .sidebar }
#### Source Code
\

The soure code of the [data.plot.left_detailed](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L448) function is shown below:
```{r eval=FALSE}
data.plot.left_detailed <- function(data, 
                                    left.n = 0,
                                    title = NULL,
                                    title.left = NULL,
                                    xname, 
                                    yname, 
                                    xlabel1 = NULL, 
                                    xlabel2 = NULL, 
                                    ylabel1 = NULL,
                                    ylabel2 = NULL,
                                    line_col1 = "blue",
                                    line_col2 = "red",
                                    normalize = FALSE) {
  if(is.null(xlabel1)) {
    xlabel1 <- xname
  }
  if(is.null(xlabel2)) {
    xlabel2 <- str_glue(xlabel1, " (left part)")
  }
  if(is.null(ylabel1)) {
    ylabel1 <- yname
  }
  if(is.null(ylabel2)) {
    ylabel2 <- ylabel1
  }

  p1 <- data |>
    data.plot(title = title,
              xname = xname, 
              yname = yname, 
              xlabel = xlabel1, 
              ylabel = ylabel1,
              line_col = line_col1)

  p2 <- data |>
    data.plot.left.n(left.n = left.n,
                     title = title.left,
                     xname = xname, 
                     yname = yname, 
                     xlabel = xlabel2, 
                     ylabel = ylabel2,
                     line_col = line_col2,
                     normalize = normalize)
  grid.arrange(p1, p2)
}
```

::: {.noteblock data-latex=""}
The source code of the [data.plot.left_detailed](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L448) is also available in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L448) script.
:::
:::
